\tool: Revisiting BadUSB with Type-C

### 2021-03-19 WOOT/Files/experiment.tex
version

\begin{table*}[t]
	\centering
	\begin{tabular}{|c|c|l|l|c|c|}
		\hline
		\multirow{2}{*}{\textbf{Category} } & \multirow{2}{*}{ \textbf{Application} } & \multicolumn{2}{c|}{\textbf{Leaked Sensitive Information}} \\
															\cline{3-4}
											&				& \textbf{Without Authentication}						& \textbf{With Authentication} \\
		\hline
		Social \& Finance App 				& WeChat      & Account, Financial Status, Chat History, Payment Code   		& Payment Password \\
		\hline
		\multirow{2}{*}{Social App}
											%& QQ          & Account, Contacts, Chat History   	& \\
											%\cline{2-4}
							       			& WhatsApp    & Account, Contacts, Chat History, Phone Number    & \\
											\cline{2-4}
							       			& Facebook    & Account, Posts, Contacts           & \\
		\hline
		\multirow{3}{*}{Finance App}       	& Alipay      & Account, Financial Status, Payment Code         				& Payment Password \\
											\cline{2-4}
											& Cash App    & Email, Phone Number, Cash Balance							& Payment Password \\
											\cline{2-4}
											& Paypal      & Account, PayPal Balance     								& Payment Password \\
		\hline
		\multirow{1}{*}{Shopping App}		& Amazon Shopping  & Account, Orders, Shopping Cart         				& \\
											%\cline{2-4}
		                					%& Taobao      & Personal physical metrics      						& \\
		\hline
		\multirow{2}{*}{Tool}               & Chrome      & Browsing History                                	& \\
											\cline{2-4}
		                					& Health      & Personal Health Metrics      						& \\
		\hline
		\multirow{3}{*}{System}             &  Messages   & Contacts, Chat History				 &   \\
											\cline{2-4}
											& Settings - WiFi   & WiFi SSID                                	&  WiFi Password \\
											\cline{2-4}
		                					& Settings - VPN    & VPN Address, VPN Account, VPN Password      						& \\
		\hline
	\end{tabular}
	\linebreak
	\caption{Sensitive Information Leaked From Applications.}
	\label{table:information_extracted}
\end{table*}

>>>>

\begin{table*}[t]
	\centering
	\begin{tabular}{|c|c|l|l|c|c|}
		\hline
		\multirow{2}{*}{\textbf{Category} } & \multirow{2}{*}{ \textbf{Application} } & \multicolumn{2}{c|}{\textbf{Leaked Sensitive Information}} \\
															\cline{3-4}
											&				& \textbf{Without Victim's Interaction}						& \textbf{With Victim's Interaction} \\
		\hline
		Social \& Finance App 				& WeChat (8.0.1)      & Account, Financial Status, Chat History, Payment Code   		& Payment Password \\
		\hline
		\multirow{2}{*}{Social App}
											%& QQ          & Account, Contacts, Chat History   	& \\
											%\cline{2-4}
							       			& WhatsApp (2.21.5.18)    & Account, Contacts, Chat History, Phone Number    & \\
											\cline{2-4}
							       			& Facebook (309.0.0.47.119)   & Account, Posts, Contacts           & \\
		\hline
		\multirow{3}{*}{Finance App}       	& Alipay (10.2.15.9500)      & Account, Financial Status, Payment Code         				& Payment Password \\
											\cline{2-4}
											& Cash App (3.35.1)   & Email, Phone Number, Cash Balance							& Payment Password \\
											\cline{2-4}
											& Paypal (7.38.1)      & Account, PayPal Balance     								& Payment Password \\
		\hline
		\multirow{1}{*}{Shopping App}		& Amazon Shopping (22.6.0.100)  & Account, Orders, Shopping Cart         				& \\
											%\cline{2-4}
		                					%& Taobao      & Personal physical metrics      						& \\
		\hline
		\multirow{2}{*}{Tool}               & Chrome (89.0.4389.72)      & Browsing History                                	& \\
											\cline{2-4}
		                					& Health (11.0.5.508)      & Personal Health Metrics      						& \\
		\hline
		\multirow{3}{*}{System}             &  Messages (11.0.1.430)   & Contacts, Chat History				 &   \\
											\cline{2-4}
											& Settings (11.0.0.300) - WiFi   & WiFi SSID                                	&  WiFi Password \\
											\cline{2-4}
		                					& Settings (11.0.0.300) - VPN    & VPN Address, VPN Account, VPN Password      						& \\
		\hline
	\end{tabular}
	\linebreak
	\caption{Sensitive Information Leaked From Applications.}
	\label{table:information_extracted}
\end{table*}
